Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-14 bbbq_article.tex
Processed all Richel's notes-to-self

We grouped all epitopes presented by MHC-I and MHC-II alleles and show 
the percentage of which these were TMH-derived in figure \ref{fig:2b}.
\richel{value}\% and \richel{value}\% were
predicted to be TMH-derived epitopes.
\richel{Indeed, what is the null hypothesis? The original one is that
zero percent of all TMH derived epitopes is presented, rendering statistics
useless. However, what about testing if TMH-derived epitopes are presented
just as often as TMHs are part of the proteom?}.

The percentage of TMH derived epitopes is relatively high
for both the predictions \richel{Figure 1} 
and statistical chance \richel{indeed, need stats}, 
however these results are hard to compare with the predictions as they are biased by
(I) the expression of the probed proteins and cleavage sites, 
(II) the bias in mass spectrometry towards hydrophillic peptides (refs) and (III) availablilty of data for the different alleles.

In fact, these findings robustly confirm that
epitopes derived from human TMHs are presented in both MHC-I and MHC-II.
See the supplementary Table \ref{tab:elution} for the exact values.

We also mined the IEDB database for in
which T-cell responses were confirmed against specific human epitopes from the specified
alleles, from the total reports \richel{value}\% and \richel{value}\% concerned TMH-derived epitopes in MHC class I
and II, respectively 
(see Figure \ref{fig:t_cells_present_tmh_derived_epitopes}). 
This data confirms that not only TMH derived epitopes are presented on MHC, but also result in immune responses.

@@

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles 
    that overlap with TMHs that are presented
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    \textbf{(B)} 
    MHC ligands from the IEDB bind to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay
    \richel{Numbers must be 8031 and 698, percentage will then match 2A}
  }
  \label{fig:elution}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Elution studies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

See figure \ref{fig:elution_per_software} or
supplementary Table \ref{tab:elution} 
for the percentages of epitopes derived from a TMH 
found in the two elution studies, 
for the two different kind of topology prediction tools.

@@

In the main text of this research, we use two sources of epitopes
to determine if TMH-derived epitopes are presented.
The first source of epitopes are all the 9-mers (for MHC-I) (and 15-mers for MHC-II)
derived from a human reference proteome, where this over-presentation
is displayed in figure \ref{fig:bbbq_1_smart_results}.
The second source of epitopes are those that are present in the IEDB
that are obtained from MHC ligand assays,
as displayed in figure \ref{fig:2a}.

>>>>

We grouped all epitopes presented by MHC-I and MHC-II alleles and show 
the percentage of which these were TMH-derived in figure \ref{fig:2b},
which are 22\% and 10\%.

The percentage of TMH derived epitopes is relatively high
for both sources of epitopes, which are (1) the predicted 
9-mers (for MHC-I) and 14-mers (for MHC-II) from
a reference human proteome  (see Figure \ref{fig:bbbq_1_smart_results}),
(2) the IEBD epitopes from MHC ligand assays (Figure \ref{fig:2a}).
These results cannot be compared with an \emp{a priori}
expactation, as the predicted percentages are biased by
(I) the expression of the probed proteins and cleavage sites, 
(II) the bias in mass spectrometry towards hydrophillic peptides 
and (III) availablilty of data for the different alleles.

Regardless, these findings robustly confirm that
epitopes derived from human TMHs are presented in both MHC-I and MHC-II.
See the supplementary Table \ref{tab:elution} for the exact values.

We also mined the IEDB database for in
which T-cell responses were confirmed against specific human epitopes from the specified
alleles, from the total reports 36\% and 7\% 
concerned TMH-derived epitopes in MHC class I and II, respectively 
(see Figure \ref{fig:t_cells_present_tmh_derived_epitopes}).

This data confirms that not only TMH derived epitopes are presented on MHC, but also result in immune responses.

@@

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles 
    that overlap with TMHs that are presented
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    \textbf{(B)} 
    MHC ligands from the IEDB bind to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay
  }
  \label{fig:elution}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The percentage of TMH-derived epitopes from IEDB epitopes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We display the over-presentation of epitopes taken from the
IEDB database, for two assays: an MHC ligand assay (Figure \ref{fig:2a})
and a T cell assay (see figure \ref{fig:t_cells_present_tmh_derived_epitopes}),
as a bar plot.
Supplementary Table \ref{tab:elution} below shows the
exact numbers.

@@

In the main text of this research, we use two sources of epitopes
to determine if TMH-derived epitopes are presented.
The first source of epitopes are all the 9-mers (for MHC-I) (and 14-mers for MHC-II)
derived from a human reference proteome, where this over-presentation
is displayed in figure \ref{fig:bbbq_1_smart_results}.
The second source of epitopes are those that are present in the IEDB
that are obtained from MHC ligand assays,
as displayed in figure \ref{fig:2a}.
